Trajectories

### 2021-09-20 Rmd/report.Rmd
Fix report GT tables

```{r participants_edu, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants %>%
  mutate(edu_parent = fct_explicit_na(as.factor(edu_parent))) %>% 
  count(lp, dominant_language, edu_parent) %>% 
  right_join(
    expand_grid(
      lp = c("Monolingual", "Bilingual"),
      dominant_language = c("Catalan", "Spanish"),
      edu_parent = unique(participants$edu_parent)
    )
  ) %>% 
  replace_na(list(n = 0)) %>% 
  pivot_wider(names_from = edu_parent, values_from = n, values_fill = 0) %>%
  mutate(n = rowSums(cbind(.[,3:8]))) %>% 
  select(-"NA") %>% 
  gt() %>% 
  cols_label(
    lp = "Lang. Profile",
    dominant_language = "L1"
  ) %>% 
  summary_rows(
    columns = 3:8,
    fns = list(n = ~sum(.)),
    formatter = fmt_number,
    decimals = 0
  ) %>% 
  tab_style(
    style = list(cell_borders(weight = px(2), sides = "left")),
    locations = cells_body(columns = 10, rows = 1:4)
  )
```

>>>>

```{r participants_edu, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants %>%
  mutate(edu_parent = fct_explicit_na(as.factor(edu_parent))) %>% 
  count(lp, dominant_language, edu_parent) %>% 
  right_join(
    expand_grid(
      lp = c("Monolingual", "Bilingual"),
      dominant_language = c("Catalan", "Spanish"),
      edu_parent = unique(participants$edu_parent)
    )
  ) %>% 
  replace_na(list(n = 0)) %>% 
  pivot_wider(names_from = edu_parent, values_from = n, values_fill = 0) %>%
  mutate(n = rowSums(cbind(.[,3:8]))) %>% 
  select(-"NA") %>% 
  gt() %>% 
  cols_label(
    lp = "Lang. Profile",
    dominant_language = "L1"
  ) %>% 
  summary_rows(
    columns = 3:8,
    fns = list(n = ~sum(.)),
    formatter = fmt_number,
    decimals = 0
  ) %>% 
  tab_style(
    style = list(cell_borders(weight = px(2), sides = "left")),
    locations = cells_body(columns = 10, rows = 1:4)
  ) %>%
  as_raw_html()
```
